Digital Twins for Ocean Robots

### 2024-11-29 paper/paper.tex
cosmetic improvements (3)

\begin{lstlisting}[
    language = Julia,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. 
    Visualization code is provided in the \pkg{Drifters.jl} documentation.}
]

using OceanRobots, Drifters, CairoMakie ;
P=Drifters.Gulf_of_Mexico_setup();
F=FlowFields(u=P.u,v=P.v,period=P.T);
I=Individuals(F,P.x0,P.y0);
[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt];
\end{lstlisting}

>>>>

\begin{lstlisting}[
    language = Julia,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. 
    Visualization code is provided in the \pkg{Drifters.jl} documentation.}
]
using OceanRobots, Drifters, CairoMakie ;
P=Drifters.Gulf_of_Mexico_setup();
F=FlowFields(u=P.u,v=P.v,period=P.T);
I=Individuals(F,P.x0,P.y0);
[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt];
\end{lstlisting}
